---
title: "MAPS - SRTS for STREETS Study: Cleaning and Scoring"
author: "LAG"
date: "Last modified 2-28-2022"
output: html_document
---

```{r setup, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(irr)
library(rlang)
library(reshape2)

```
Instructions for MAPS-SRTS Scoring Code:
- This code is set up to handle up to 4 school access segments, 14 segments, and 10 crossings.
- If your data set has less than these limits, please delete or add to the scoring code blocks for school access segment scoring (# 3), segment scoring (#4), and crossing scoring (#5) to match the upper limit of these sections in your data. You can determine how many school access segments, segments, and crossings are in your data set using code block #2. 
```{r 1. Import data}
# Import CSV with 1 observation per row
maps <- read.csv("/Users/leighannganzar/Desktop/Post-Doc/Projects/MAPS/MAPS-SRTS/all_observations_clean_1-11-22.csv")
```

```{r For STREETS: Recode school access segment variables}
# transit
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A101", "A201", "A301", "A401"), list(~recode(.,`1`=0, `0`=1)))

# sidewalk adjacent to parking lot
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A104", "A204", "A304", "A404"), list(~recode(.,`0`=3, `1`=2, `2`=1, `3`=0, `4`=-777)))

# width of sidewalk
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A108", "A208", "A308", "A408"), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=-777)))

# poorly maintained sidewalk
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A109", "A209", "A309", "A409"), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=4, `4`=-777)))

# buffer present
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A110", "A210", "A310", "A410"), list(~recode(.,`0`=0, `1`=1, `2`=-777)))

# tree canopy
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A111", "A211", "A311", "A411"), list(~recode(.,`0`=0, `1`=1, `2`=2, `3`=-777)))

# awnings
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A112", "A212", "A312", "A412"), list(~recode(.,`0`=0, `1`=1, `2`=2, `3`=-777)))

# posted speed limit
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A113", "A213", "A313", "A413"), list(~recode(.,`0`=5, `1`=4, `2`=3, `3`=2, `4`=1, `5`=0)))

# speed restrictions
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A114", "A214", "A314", "A414"), list(~recode(.,`0`=3, `1`=2, `2`=1, `3`=0)))

# signage maintenance and land use
maps <- maps %>%
  rename("A118a" = "A118_0",
         "A118b" = "A118_1",
         "A118c" = "A118_2",
         "A118d" = "A118_3",
         "A118e" = "A118_4",
         "A218a" = "A218_0",
         "A218b" = "A218_1",
         "A218c" = "A218_2",
         "A218d" = "A218_3",
         "A218e" = "A218_4",
         "A318a" = "A318_0",
         "A318b" = "A318_1",
         "A318c" = "A318_2",
         "A318d" = "A318_3",
         "A318e" = "A318_4",
         "A418a" = "A418_0",
         "A418b" = "A418_1",
         "A418c" = "A418_2",
         "A418d" = "A418_3",
         "A418e" = "A418_4",
         "A119a" = "A119_0",
         "A119b" = "A119_1",
         "A119c" = "A119_2",
         "A119d" = "A119_3",
         "A219a" = "A219_0",
         "A219b" = "A219_1",
         "A219c" = "A219_2",
         "A219d" = "A219_3",
         "A319a" = "A319_0",
         "A319b" = "A319_1",
         "A319c" = "A319_2",
         "A319d" = "A319_3",
         "A419a" = "A419_0",
         "A419b" = "A419_1",
         "A419c" = "A419_2",
         "A419d" = "A419_3")

# driveways
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(c("A121", "A221", "A321", "A421"), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=4)))
```

```{r For STREETS: Recode segment variables}
# rename S1315c 
maps <- maps %>%
  rename("S1315c" = "X1315c")
# add S1420
maps$S1420 <- NA

# transit
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("01")), list(~recode(.,`1`=0, `0`=1)))

# sidewalk adjacent to parking lot
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("04")), list(~recode(.,`0`=3, `1`=2, `2`=1, `3`=0, `4`=-777)))

# width of sidewalk
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("08")), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=-777)))

# poorly maintained sidewalk
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("09")), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=4, `4`=-777)))

# buffer present
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("10")), list(~recode(.,`0`=0, `1`=1, `2`=-777)))

# tree canopy
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("11")), list(~recode(.,`0`=0, `1`=1, `2`=2, `3`=-777)))

# awnings
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("12")), list(~recode(.,`0`=0, `1`=1, `2`=2, `3`=-777)))

# posted speed limit
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("13a")), list(~recode(.,`0`=5, `1`=4, `2`=3, `3`=2, `4`=1, `5`=0)))

# posted speed limit - spec zone
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("13b")), list(~recode(.,`0`=5, `1`=4, `2`=3, `3`=2, `4`=1, `5`=0)))

# signage maintenance
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("16")), list(~recode(.,`0`=0, `1`=1, `2`=2, `3`=3, `4`=-777)))

# driveways
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("S") & ends_with("19")), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=4)))

# signage 
maps <- maps %>%
  rename("S116a" = "S116_0",
         "S116b" = "S116_1",
         "S116c" = "S116_2",
         "S116d" = "S116_3",
         "S116e" = "S116_4",
         "S216a" = "S216_0",
         "S216b" = "S216_1",
         "S216c" = "S216_2",
         "S216d" = "S216_3",
         "S216e" = "S216_4",
         "S316a" = "S316_0",
         "S316b" = "S316_1",
         "S316c" = "S316_2",
         "S316d" = "S316_3",
         "S316e" = "S316_4",
         "S416a" = "S416_0",
         "S416b" = "S416_1",
         "S416c" = "S416_2",
         "S416d" = "S416_3",
         "S416e" = "S416_4",
         "S516a" = "S516_0",
         "S516b" = "S516_1",
         "S516c" = "S516_2",
         "S516d" = "S516_3",
         "S516e" = "S516_4",
         "S616a" = "S616_0",
         "S616b" = "S616_1",
         "S616c" = "S616_2",
         "S616d" = "S616_3",
         "S616e" = "S616_4",
         "S716a" = "S716_0",
         "S716b" = "S716_1",
         "S716c" = "S716_2",
         "S716d" = "S716_3",
         "S716e" = "S716_4",
         "S816a" = "S816_0",
         "S816b" = "S816_1",
         "S816c" = "S816_2",
         "S816d" = "S816_3",
         "S816e" = "S816_4",
         "S916a" = "S916_0",
         "S916b" = "S916_1",
         "S916c" = "S916_2",
         "S916d" = "S916_3",
         "S916e" = "S916_4",
         "S1016a" = "S1016_0",
         "S1016b" = "S1016_1",
         "S1016c" = "S1016_2",
         "S1016d" = "S1016_3",
         "S1016e" = "S1016_4",
         "S1116a" = "S1116_0",
         "S1116b" = "S1116_1",
         "S1116c" = "S1116_2",
         "S1116d" = "S1116_3",
         "S1116e" = "S1116_4",
         "S1216a" = "S1216_0",
         "S1216b" = "S1216_1",
         "S1216c" = "S1216_2",
         "S1216d" = "S1216_3",
         "S1216e" = "S1216_4",
         "S1316a" = "S1316_0",
         "S1316b" = "S1316_1",
         "S1316c" = "S1316_2",
         "S1316d" = "S1316_3",
         "S1316e" = "S1316_4",
         "S1416a" = "S1416_0",
         "S1416b" = "S1416_1",
         "S1416c" = "S1416_2",
         "S1416d" = "S1416_3",
         "S1416e" = "S1416_4",
         "S1516a" = "S1516_0",
         "S1516b" = "S1516_1",
         "S1516c" = "S1516_2",
         "S1516d" = "S1516_3",
         "S1516e" = "S1516_4",
         "S1616a" = "S1616_0",
         "S1616b" = "S1616_1",
         "S1616c" = "S1616_2",
         "S1616d" = "S1616_3",
         "S1616e" = "S1616_4",
         "S1716a" = "S1716_0",
         "S1716b" = "S1716_1",
         "S1716c" = "S1716_2",
         "S1716d" = "S1716_3",
         "S1716e" = "S1716_4",
         "S1816a" = "S1816_0",
         "S1816b" = "S1816_1",
         "S1816c" = "S1816_2",
         "S1816d" = "S1816_3",
         "S1816e" = "S1816_4",
         "S1916a" = "S1916_0",
         "S1916b" = "S1916_1",
         "S1916c" = "S1916_2",
         "S1916d" = "S1916_3",
         "S1916e" = "S1916_4",
         "S2016a" = "S2016_0",
         "S2016b" = "S2016_1",
         "S2016c" = "S2016_2",
         "S2016d" = "S2016_3",
         "S2016e" = "S2016_4")

# land Use recode S117_0	S117_1	S117_2	S117_3
maps <- maps %>%
  rename("S117a" = "S117_0",
         "S117b" = "S117_1",
         "S117c" = "S117_2",
         "S117d" = "S117_3",
         "S217a" = "S217_0",
         "S217b" = "S217_1",
         "S217c" = "S217_2",
         "S217d" = "S217_3",
         "S317a" = "S317_0",
         "S317b" = "S317_1",
         "S317c" = "S317_2",
         "S317d" = "S317_3",
         "S417a" = "S417_0",
         "S417b" = "S417_1",
         "S417c" = "S417_2",
         "S417d" = "S417_3",
         "S517a" = "S517_0",
         "S517b" = "S517_1",
         "S517c" = "S517_2",
         "S517d" = "S517_3",
         "S617a" = "S617_0",
         "S617b" = "S617_1",
         "S617c" = "S617_2",
         "S617d" = "S617_3",
         "S717a" = "S717_0",
         "S717b" = "S717_1",
         "S717c" = "S717_2",
         "S717d" = "S717_3",
         "S817a" = "S817_0",
         "S817b" = "S817_1",
         "S817c" = "S817_2",
         "S817d" = "S817_3",
         "S917a" = "S917_0",
         "S917b" = "S917_1",
         "S917c" = "S917_2",
         "S917d" = "S917_3",
         "S1017a" = "S1017_0",
         "S1017b" = "S1017_1",
         "S1017c" = "S1017_2",
         "S1017d" = "S1017_3",
         "S1117a" = "S1117_0",
         "S1117b" = "S1117_1",
         "S1117c" = "S1117_2",
         "S1117d" = "S1117_3",
         "S1217a" = "S1217_0",
         "S1217b" = "S1217_1",
         "S1217c" = "S1217_2",
         "S1217d" = "S1217_3",
         "S1317a" = "S1317_0",
         "S1317b" = "S1317_1",
         "S1317c" = "S1317_2",
         "S1317d" = "S1317_3",
         "S1417a" = "S1417_0",
         "S1417b" = "S1417_1",
         "S1417c" = "S1417_2",
         "S1417d" = "S1417_3",
         "S1517a" = "S1517_0",
         "S1517b" = "S1517_1",
         "S1517c" = "S1517_2",
         "S1517d" = "S1517_3",
         "S1617a" = "S1617_0",
         "S1617b" = "S1717_1",
         "S1617c" = "S1617_2",
         "S1617d" = "S1617_3",
         "S1717a" = "S1617_0",
         "S1717b" = "S1717_1",
         "S1717c" = "S1717_2",
         "S1717d" = "S1717_3",
         "S1817a" = "S1817_0",
         "S1817b" = "S1817_1",
         "S1817c" = "S1817_2",
         "S1817d" = "S1817_3",
         "S1917a" = "S1917_0",
         "S1917b" = "S1917_1",
         "S1917c" = "S1917_2",
         "S1917d" = "S1917_3",
         "S2017a" = "S2017_0",
         "S2017b" = "S2017_1",
         "S2017c" = "S2017_2",
         "S2017d" = "S2017_3")
```

```{r For STREETS: Recode crossing variables}
# rename S1003a and S1003b to C
maps <- maps %>%
  rename("C1003a" = "S1003a",
         "C1003b" = "S1003b",
         "C205c" = "Q1403",
         "C300Crossing3" = "Q1400",
         "C800intersection2" = "CIntersection2") %>%
  select(-c("C500Crossing2...Topics"))

# crossing at intersection
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("C") & ends_with("01bi")), list(~recode(.,`4`=1, `5`=0)))

# pre curb
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("C") & ends_with("04a")), list(~recode(.,`2`=1, `1`=2, `0`=3)))

# post curb
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("C") & ends_with("04b")), list(~recode(.,`2`=1, `1`=2, `0`=3)))

# travel lanes
maps <- maps %>%
  mutate_if(is.logical, as.character) %>%
  mutate_at(vars(starts_with("C") & ends_with("07")), list(~recode(.,`0`=1, `1`=2, `2`=3, `3`=4, `4`=5, `5`=6, `6`=7 )))

```

```{r For STREETS: Rename all variables from STREETS Qualtrics to match data dictionary}
# Manually rename school access segment 1
maps <- maps %>%
  rename("A1_00Street" = "A100Street",
         "A1_00Side" = "A100Side",
         "A1_00Start" = "A100Start",
         "A1_00End" = "A100End",
         "A1_01" = "A101",
         "A1_02" = "A102",
         "A1_03" = "A103",
         "A1_04" = "A104",
         "A1_05" = "A105",
         "A1_06" = "A106",
         "A1_07" = "A107",
         "A1_08" = "A108",
         "A1_09" = "A109",
         "A1_10" = "A110",
         "A1_11" = "A111",
         "A1_12" = "A112",
         "A1_13" = "A113",
         "A1_14" =  "A114",
         "A1_15a" = "A115a",
         "A1_15b" = "A115b",
         "A1_16a" = "A116a",
         "A1_16b" = "A116b",
         "A1_16c" = "A116c",
         "A1_16d" = "A116d",
         "A1_17a" = "A117a",
         "A1_17b" = "A117b",
         "A1_17c" = "A117c",
         "A1_17d" = "A117d",
         "A1_17e" = "A117e",
         "A1_17f" = "A117f",
         "A1_18a" = "A118a",
         "A1_18b" = "A118b",
         "A1_18c" = "A118c",
         "A1_18d" = "A118d",
         "A1_18e" = "A118e",
         "A1_19a" = "A119a",
         "A1_19b" = "A119b",
         "A1_19c" = "A119c",
         "A1_19d" = "A119d",
         "A1_20a" = "A120a",
         "A1_20b" = "A120b",
         "A1_20c" = "A120c",
         "A1_21" = "A121",
         "A1_22" = "A122",
         "A1_00Notes" = "A100Notes")

# Create function to change prefix of variable names
change_prefix <- function(df, oldpref, newpref) {
  df %>%
       rename_at(vars(starts_with(oldpref)), funs(sub(oldpref, newpref, .)))
}
# School access segments 2 - 4 using function
maps <- change_prefix(maps, "A2", "A2_")
maps <- change_prefix(maps, "A3", "A3_")
maps <- change_prefix(maps, "A4", "A4_")

# Manually rename segments 1 & 2
maps <- maps %>%
  rename("S1_00Street" = "S100Street",
         "S1_00Side" = "S100Side",
         "S1_00Start" = "S100Start",
         "S1_00End" = "S100End",
         "S1_01" = "S101",
         "S1_02" = "S102",
         "S1_03" = "S103",
         "S1_04" = "S104",
         "S1_05" = "S105",
         "S1_06" = "S106",
         "S1_07" = "S107",
         "S1_08" = "S108",
         "S1_09" = "S109",
         "S1_10" = "S110",
         "S1_11" = "S111",
         "S1_12" = "S112",
         "S1_13a" = "S113a",
         "S1_13b" = "S113b",
         "S1_14a" = "S114a",
         "S1_14b" = "S114b",
         "S1_14c" = "S114c",
         "S1_14d" = "S114d",
         "S1_15a" = "S115a",
         "S1_15b" = "S115b",
         "S1_15c" = "S115c",
         "S1_15d" = "S115d",
         "S1_15e" = "S115e",
         "S1_15f" = "S115f",
         "S1_16a" = "S116a",
         "S1_16b" = "S116b",
         "S1_16c" = "S116c",
         "S1_16d" = "S116d",
         "S1_16e" = "S116e",
         "S1_17a" = "S117a",
         "S1_17b" = "S117b",
         "S1_17c" = "S117c",
         "S1_17d" = "S117d",
         "S1_18a" = "S118a",
         "S1_18b" = "S118b",
         "S1_18c" = "S118c",
         "S1_19" = "S119",
         "S1_20" = "S120",
         "S2_00Street" = "S200Street",
         "S2_00Side" = "S200Side",
         "S2_00Start" = "S200Start",
         "S2_00End" = "S200End",
         "S2_01" = "S201",
         "S2_02" = "S202",
         "S2_03" = "S203",
         "S2_04" = "S204",
         "S2_05" = "S205",
         "S2_06" = "S206",
         "S2_07" = "S207",
         "S2_08" = "S208",
         "S2_09" = "S209",
         "S2_10" = "S210",
         "S2_11" = "S211",
         "S2_12" = "S212",
         "S2_13a" = "S213a",
         "S2_13b" = "S213b",
         "S2_14a" = "S214a",
         "S2_14b" = "S214b",
         "S2_14c" = "S214c",
         "S2_14d" = "S214d",
         "S2_15a" = "S215a",
         "S2_15b" = "S215b",
         "S2_15c" = "S215c",
         "S2_15d" = "S215d",
         "S2_15e" = "S215e",
         "S2_15f" = "S215f",
         "S2_16a" = "S216a",
         "S2_16b" = "S216b",
         "S2_16c" = "S216c",
         "S2_16d" = "S216d",
         "S2_16e" = "S216e",
         "S2_17a" = "S217a",
         "S2_17b" = "S217b",
         "S2_17c" = "S217c",
         "S2_17d" = "S217d",
         "S2_18a" = "S218a",
         "S2_18b" = "S218b",
         "S2_18c" = "S218c",
         "S2_19" = "S219",
         "S2_20" = "S220")

# Segments 3 - 20 using function
maps <- change_prefix(maps, "S20", "S20_")
maps <- change_prefix(maps, "S19", "S19_")
maps <- change_prefix(maps, "S18", "S18_")
maps <- change_prefix(maps, "S17", "S17_")
maps <- change_prefix(maps, "S16", "S16_")
maps <- change_prefix(maps, "S15", "S15_")
maps <- change_prefix(maps, "S14", "S14_")
maps <- change_prefix(maps, "S13", "S13_")
maps <- change_prefix(maps, "S12", "S12_")
maps <- change_prefix(maps, "S11", "S11_")
maps <- change_prefix(maps, "S10", "S10_")
maps <- change_prefix(maps, "S9", "S9_")
maps <- change_prefix(maps, "S8", "S8_")
maps <- change_prefix(maps, "S7", "S7_")
maps <- change_prefix(maps, "S6", "S6_")
maps <- change_prefix(maps, "S5", "S5_")
maps <- change_prefix(maps, "S4", "S4_")
maps <- change_prefix(maps, "S3", "S3_")

# Manually rename crossing 1 & 2
maps <- maps %>%
  rename("C1_01a" = "C101a",
         "C1_01b" = "C101b",
         "C1_01bi" = "C101bi",
         "C1_00Intersection1" = "C100Intersection1",
         "C1_00Intersection2" = "C100Intersection2",
         "C1_00Direction1" = "C100Direction1",
         "C1_00Direction2" = "C100Direction2",
         "C1_01bii" = "C101bii",
         "C1_01c" = "C101c",
         "C1_00Crossing1" = "C100Crossing1",
         "C1_00Crossing2" = "C100Crossing2",
         "C1_00Crossing3" = "C100Crossing3",
         "C1_02a" = "C102a",
         "C1_02b" = "C102b",
         "C1_02c" = "C102c",
         "C1_02d" = "C102d",
         "C1_03a" = "C103a",
         "C1_03b" = "C103b",
         "C1_03c" = "C103c",
         "C1_03d" = "C103d",
         "C1_04a" = "C104a",
         "C1_04b" = "C104b",
         "C1_05a" = "C105a",
         "C1_05b" = "C105b",
         "C1_05c" = "C105c",
         "C1_05d" = "C105d",
         "C1_06a" = "C106a",
         "C1_06b" = "C106b",
         "C1_06c" = "C106c",
         "C1_07" = "C107",
         "C1_08" = "C108",
         "C1_09a" = "C109a",
         "C1_09b" = "C109b",
         "C1_09c" = "C109c",
         "C1_00Notes" = "C100Notes")

# Crossing 2 - 10 using function
maps <- change_prefix(maps, "C10", "C10_")
maps <- change_prefix(maps, "C9", "C9_")
maps <- change_prefix(maps, "C8", "C8_")
maps <- change_prefix(maps, "C7", "C7_")
maps <- change_prefix(maps, "C6", "C6_")
maps <- change_prefix(maps, "C5", "C5_")
maps <- change_prefix(maps, "C4", "C4_")
maps <- change_prefix(maps, "C3", "C3_")
maps <- change_prefix(maps, "C2", "C2_")
```

```{r 2. Create variables for number of SAS, segments, and crossings}
# Determine number of school access segments, segments, and crossings per school
maps <- maps %>%
  mutate(number_A = case_when(is.na(A4_01) & is.na(A3_01) & is.na(A2_01) ~ 1,
                              is.na(A4_01) & is.na(A3_01) ~ 2, 
                              is.na(A4_01) ~ 3,
                              TRUE ~ 4),
         number_S = case_when(is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) & is.na(S10_01) & is.na(S9_01) &
                                is.na(S8_01) & is.na(S7_01) & is.na(S6_01) ~ 5,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) & is.na(S10_01) & is.na(S9_01) &
                                is.na(S8_01) & is.na(S7_01) ~ 6,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) & is.na(S10_01) & is.na(S9_01) &
                                is.na(S8_01)~ 7,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) & is.na(S10_01) & is.na(S9_01) ~ 8,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) & is.na(S10_01) ~ 9,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) &
                                is.na(S11_01) ~ 10,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) & is.na(S12_01) ~ 11,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) & is.na(S13_01) ~ 12,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) &
                                is.na(S14_01) ~ 13,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) & is.na(S15_01) ~ 14,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) & is.na(S16_01) ~ 15,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) & 
                                is.na(S17_01) ~ 16,
                              is.na(S20_01) & is.na(S19_01) & is.na(S18_01) ~ 17,
                              is.na(S20_01) & is.na(S19_01) ~ 18,
                              is.na(S20_01) ~ 19,
                              TRUE ~ 20),
         number_C = case_when(is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) &
                                is.na(C7_02a) & is.na(C6_02a) & is.na(C5_02a) &
                                is.na(C4_02a) & is.na(C3_02a) ~ 2,
                              is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) &
                                is.na(C7_02a) & is.na(C6_02a) & is.na(C5_02a) &
                                is.na(C4_02a) ~ 3,
                              is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) &
                                is.na(C7_02a) & is.na(C6_02a) & is.na(C5_02a) ~ 4,
                              is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) &
                                is.na(C7_02a) & is.na(C6_02a) ~ 5,
                              is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) &
                                is.na(C7_02a) ~ 6,
                              is.na(C10_02a) & is.na(C9_02a) & is.na(C8_02a) ~ 7,
                              is.na(C10_02a) & is.na(C9_02a) ~ 8,
                              is.na(C10_02a) ~ 9,
                              TRUE ~ 10)
         )
table(maps$number_A)
table(maps$number_S)
table(maps$number_C)

# look at frequency distributions for STREETS cohort (n=36)
maps_A <- maps %>%
  filter(timepoint == 1 & cohort == 1) %>%
  summarise(mean = mean(number_A), sd = sd(number_A))
maps_A
maps_S <- maps %>%
  filter(timepoint == 1 & cohort == 1) %>%
  summarise(mean = mean(number_S), sd = sd(number_S))
maps_S
maps_C <- maps %>%
  filter(timepoint == 1 & cohort == 1) %>%
  summarise(mean = mean(number_C), sd = sd(number_C))
maps_C
```

```{r 3. Subscale scoring for school access segments}
# A1 --------------------------------------------------------------------------
# select only School Access Segment variables and rename, ensure the order of variable names matches data set
A <- maps %>% 
  select(c(starts_with("A1_"),"SchoolID" )) %>%
  setNames( c("A_00Street", "A_00Side", "A_00Start", 
              "A__00End", "A_01", "A_02","A_03", "A_04",
              "A_05", "A_06","A_07", "A_08", "A_09", 
              "A_10", "A_11", "A_12", "A_13", "A_14", 
              "A_15a", "A_15b", "A_16a", "A_16b", 
              "A_16c", "A_16d", "A_17a", "A_17b", "A_17c",
              "A_17d", "A_17e", "A_17f", "A_18a", "A_18b", 
              "A_18c", "A_18d", "A_18e", "A_19a", "A_19b",
              "A_19c", "A_19d", "A_20a", "A_20b", "A_20c", "A_21", 
              "A_22", "A_00Notes", "SchoolID"))
# Create subscales
A <- A %>%
  mutate(
    A_calming_pos = case_when(A_16a == 1 | A_16b == 1 | A_16c == 1 | A_16d == 1 ~ 1, # Positive streetscape subscale
                              A_16a == 0 & A_16b == 0 & A_16c == 0 & A_16d == 0 ~ 0),
    A_lights_pos = case_when(A_02 == 1 | A_02 == 2 | A_03 == 1 | A_03 == 2 ~ 1,
                             A_02 == 0 & A_03 == 0 ~ 0),
    A_driveways_pos = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 1,
                                A_21 == 4 ~ 0),
    A_speed_dichot = case_when(A_13 == 5 | A_13 == 4 | A_13 == 3 | A_13 == 2 | A_13 == 1 ~ 1, 
                               A_13 == 0 ~ 0),
    A_speed25_pos = case_when(A_13 == 5 | A_13 == 4 ~ 1,
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 0),
    A_speed_spec_pos = case_when(A_14 == 3 | A_14 == 2 | A_14 == 1 ~ 1,
                                    A_14 == 0 ~ 0),
    A_signs_pos = A_17a + A_17b + A_17c + A_17d,
    A_streetscape_pos = 
           A_01 + 
           A_calming_pos + 
           A_lights_pos +
           A_driveways_pos +
           A_20a +
           A_20b +
           A_20c +
           A_speed_dichot + 
           A_speed25_pos +
           A_speed_spec_pos +
           A_signs_pos,
    A_sidewalk = case_when(A_07 == 2 | A_07 == 3 ~ 2, # Positive sidewalk subscale
                           A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_cont = case_when(A_07 == 3 ~ 1,
                                A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_width = case_when(A_08 == 3 ~ 3,
                                 A_08 == 2 | A_08 == 1 ~ 2,
                                 A_08 == -777 ~ 0),
    A_sidewalk_pos = A_sidewalk + A_sidewalk_cont + A_sidewalk_width,
    A_buffer_pos = case_when(A_10 == 1 ~ 1, # Positive buffer
                             A_10 == 0 | A_10 == -777 ~ 0), 
    A_bike_pos = case_when(A_06 == 5 | A_06 == 4 ~ 2, # Bike infrastructure 
                           A_06 == 3 | A_06 == 2 ~ 1,
                           A_06 == 1 | A_06 == 0 ~ 0), 
    A_trees_pos = case_when(A_11 == 2 ~ 2, # Shade
                            A_11 == 1 ~ 1,
                            A_11 == 0 | A_11 == -777 ~ 0), 
    A_awning_pos = case_when(A_12 == 2 ~ 2,
                             A_12 == 1 ~ 1,
                             A_12 == 0 | A_12 == -777 ~ 0),
    A_shade_pos = A_trees_pos + A_awning_pos,
    A_overall_pos = A_streetscape_pos + # Positive SAS
           A_sidewalk_pos + 
           A_buffer_pos + 
           A_bike_pos + 
           A_shade_pos,
    A_speed25_neg = case_when(A_13 == 5 | A_13 == 4 ~ 0, # Negative streetscape
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 1), 
    A_driveways_neg = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 0,
                                A_21 == 4 ~ 1),
    A_streetscape_neg = A_speed25_neg + A_driveways_neg,
    A_cont_neg = case_when(A_07 == 3 ~ 0,
                           A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 1), # Negative sidewalk
    A_trip_neg = case_when(A_09 == 1 | A_09 == 2 | A_09 ==-777 ~ 0,
                           A_09 == 3 | A_09 == 4 ~ 1),
    A_sidewalk_neg = A_cont_neg + A_trip_neg, 
    A_aes_neg = case_when(A_05 == 0 ~ 0, 
                          A_05 = 1 | A_05 == 2 | A_05 == 3 ~ 1), #Negative aesthetics 
    A_overall_neg = A_streetscape_neg + A_sidewalk_neg + A_aes_neg, # Negative SAS
    A_overall = A_overall_pos - A_overall_neg # Overall SAS 1 
    )
# add A1_ prefix back to variable names
A1 <- A %>% 
  rename_with(~gsub("A_", "A1_", .x))

# A2 --------------------------------------------------------------------------
# select only School Access Segment variables and rename, ensure the order of variable names matches data set
A <- maps %>% 
  select(c(starts_with("A2_"),"SchoolID" )) %>%
  setNames( c("A_00Street", "A_00Side", "A_00Start", 
              "A__00End", "A_01", "A_02","A_03", "A_04",
              "A_05", "A_06","A_07", "A_08", "A_09", 
              "A_10", "A_11", "A_12", "A_13", "A_14", 
              "A_15a", "A_15b", "A_16a", "A_16b", 
              "A_16c", "A_16d", "A_17a", "A_17b", "A_17c",
              "A_17d", "A_17e", "A_17f", "A_18a", "A_18b", 
              "A_18c", "A_18d", "A_18e", "A_19a", "A_19b",
              "A_19c", "A_19d", "A_20a", "A_20b", "A_20c", "A_21", 
              "A_22", "A_00Notes", "SchoolID"))
# Create subscales
A <- A %>%
  mutate(
    A_calming_pos = case_when(A_16a == 1 | A_16b == 1 | A_16c == 1 | A_16d == 1 ~ 1, # Positive streetscape subscale
                              A_16a == 0 & A_16b == 0 & A_16c == 0 & A_16d == 0 ~ 0),
    A_lights_pos = case_when(A_02 == 1 | A_02 == 2 | A_03 == 1 | A_03 == 2 ~ 1,
                             A_02 == 0 & A_03 == 0 ~ 0),
    A_driveways_pos = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 1,
                                A_21 == 4 ~ 0),
    A_speed_dichot = case_when(A_13 == 5 | A_13 == 4 | A_13 == 3 | A_13 == 2 | A_13 == 1 ~ 1, 
                               A_13 == 0 ~ 0),
    A_speed25_pos = case_when(A_13 == 5 | A_13 == 4 ~ 1,
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 0),
    A_speed_spec_pos = case_when(A_14 == 3 | A_14 == 2 | A_14 == 1 ~ 1,
                                    A_14 == 0 ~ 0),
    A_signs_pos = A_17a + A_17b + A_17c + A_17d,
    A_streetscape_pos = 
           A_01 + 
           A_calming_pos + 
           A_lights_pos +
           A_driveways_pos +
           A_20a +
           A_20b +
           A_20c +
           A_speed_dichot + 
           A_speed25_pos +
           A_speed_spec_pos +
           A_signs_pos,
    A_sidewalk = case_when(A_07 == 2 | A_07 == 3 ~ 2, # Positive sidewalk subscale
                           A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_cont = case_when(A_07 == 3 ~ 1,
                                A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_width = case_when(A_08 == 3 ~ 3,
                                 A_08 == 2 | A_08 == 1 ~ 2,
                                 A_08 == -777 ~ 0),
    A_sidewalk_pos = A_sidewalk + A_sidewalk_cont + A_sidewalk_width,
    A_buffer_pos = case_when(A_10 == 1 ~ 1, # Positive buffer
                             A_10 == 0 | A_10 == -777 ~ 0), 
    A_bike_pos = case_when(A_06 == 5 | A_06 == 4 ~ 2, # Bike infrastructure 
                           A_06 == 3 | A_06 == 2 ~ 1,
                           A_06 == 1 | A_06 == 0 ~ 0), 
    A_trees_pos = case_when(A_11 == 2 ~ 2, # Shade
                            A_11 == 1 ~ 1,
                            A_11 == 0 | A_11 == -777 ~ 0), 
    A_awning_pos = case_when(A_12 == 2 ~ 2,
                             A_12 == 1 ~ 1,
                             A_12 == 0 | A_12 == -777 ~ 0),
    A_shade_pos = A_trees_pos + A_awning_pos,
    A_overall_pos = A_streetscape_pos + # Positive SAS
           A_sidewalk_pos + 
           A_buffer_pos + 
           A_bike_pos + 
           A_shade_pos,
    A_speed25_neg = case_when(A_13 == 5 | A_13 == 4 ~ 0, # Negative streetscape
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 1), 
    A_driveways_neg = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 0,
                                A_21 == 4 ~ 1),
    A_streetscape_neg = A_speed25_neg + A_driveways_neg,
    A_cont_neg = case_when(A_07 == 3 ~ 0,
                           A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 1), # Negative sidewalk
    A_trip_neg = case_when(A_09 == 1 | A_09 == 2 | A_09 ==-777 ~ 0,
                           A_09 == 3 | A_09 == 4 ~ 1),
    A_sidewalk_neg = A_cont_neg + A_trip_neg, 
    A_aes_neg = case_when(A_05 == 0 ~ 0, 
                          A_05 = 1 | A_05 == 2 | A_05 == 3 ~ 1), #Negative aesthetics 
    A_overall_neg = A_streetscape_neg + A_sidewalk_neg + A_aes_neg, # Negative SAS
    A_overall = A_overall_pos - A_overall_neg # Overall SAS 1 
    )
# add A2_ prefix back to variable names
A2 <- A %>% 
  rename_with(~gsub("A_", "A2_", .x))

# A3 --------------------------------------------------------------------------
# select only School Access Segment variables and rename, ensure the order of variable names matches data set
A <- maps %>% 
  select(c(starts_with("A3_"),"SchoolID" )) %>%
  setNames( c("A_00Street", "A_00Side", "A_00Start", 
              "A__00End", "A_01", "A_02","A_03", "A_04",
              "A_05", "A_06","A_07", "A_08", "A_09", 
              "A_10", "A_11", "A_12", "A_13", "A_14", 
              "A_15a", "A_15b", "A_16a", "A_16b", 
              "A_16c", "A_16d", "A_17a", "A_17b", "A_17c",
              "A_17d", "A_17e", "A_17f", "A_18a", "A_18b", 
              "A_18c", "A_18d", "A_18e", "A_19a", "A_19b",
              "A_19c", "A_19d", "A_20a", "A_20b", "A_20c", "A_21", 
              "A_22", "A_00Notes", "SchoolID"))
# Create subscales
A <- A %>%
  mutate(
    A_calming_pos = case_when(A_16a == 1 | A_16b == 1 | A_16c == 1 | A_16d == 1 ~ 1, # Positive streetscape subscale
                              A_16a == 0 & A_16b == 0 & A_16c == 0 & A_16d == 0 ~ 0),
    A_lights_pos = case_when(A_02 == 1 | A_02 == 2 | A_03 == 1 | A_03 == 2 ~ 1,
                             A_02 == 0 & A_03 == 0 ~ 0),
    A_driveways_pos = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 1,
                                A_21 == 4 ~ 0),
    A_speed_dichot = case_when(A_13 == 5 | A_13 == 4 | A_13 == 3 | A_13 == 2 | A_13 == 1 ~ 1, 
                               A_13 == 0 ~ 0),
    A_speed25_pos = case_when(A_13 == 5 | A_13 == 4 ~ 1,
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 0),
    A_speed_spec_pos = case_when(A_14 == 3 | A_14 == 2 | A_14 == 1 ~ 1,
                                    A_14 == 0 ~ 0),
    A_signs_pos = A_17a + A_17b + A_17c + A_17d,
    A_streetscape_pos = 
           A_01 + 
           A_calming_pos + 
           A_lights_pos +
           A_driveways_pos +
           A_20a +
           A_20b +
           A_20c +
           A_speed_dichot + 
           A_speed25_pos +
           A_speed_spec_pos +
           A_signs_pos,
    A_sidewalk = case_when(A_07 == 2 | A_07 == 3 ~ 2, # Positive sidewalk subscale
                           A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_cont = case_when(A_07 == 3 ~ 1,
                                A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_width = case_when(A_08 == 3 ~ 3,
                                 A_08 == 2 | A_08 == 1 ~ 2,
                                 A_08 == -777 ~ 0),
    A_sidewalk_pos = A_sidewalk + A_sidewalk_cont + A_sidewalk_width,
    A_buffer_pos = case_when(A_10 == 1 ~ 1, # Positive buffer
                             A_10 == 0 | A_10 == -777 ~ 0), 
    A_bike_pos = case_when(A_06 == 5 | A_06 == 4 ~ 2, # Bike infrastructure 
                           A_06 == 3 | A_06 == 2 ~ 1,
                           A_06 == 1 | A_06 == 0 ~ 0), 
    A_trees_pos = case_when(A_11 == 2 ~ 2, # Shade
                            A_11 == 1 ~ 1,
                            A_11 == 0 | A_11 == -777 ~ 0), 
    A_awning_pos = case_when(A_12 == 2 ~ 2,
                             A_12 == 1 ~ 1,
                             A_12 == 0 | A_12 == -777 ~ 0),
    A_shade_pos = A_trees_pos + A_awning_pos,
    A_overall_pos = A_streetscape_pos + # Positive SAS
           A_sidewalk_pos + 
           A_buffer_pos + 
           A_bike_pos + 
           A_shade_pos,
    A_speed25_neg = case_when(A_13 == 5 | A_13 == 4 ~ 0, # Negative streetscape
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 1), 
    A_driveways_neg = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 0,
                                A_21 == 4 ~ 1),
    A_streetscape_neg = A_speed25_neg + A_driveways_neg,
    A_cont_neg = case_when(A_07 == 3 ~ 0,
                           A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 1), # Negative sidewalk
    A_trip_neg = case_when(A_09 == 1 | A_09 == 2 | A_09 ==-777 ~ 0,
                           A_09 == 3 | A_09 == 4 ~ 1),
    A_sidewalk_neg = A_cont_neg + A_trip_neg, 
    A_aes_neg = case_when(A_05 == 0 ~ 0, 
                          A_05 = 1 | A_05 == 2 | A_05 == 3 ~ 1), #Negative aesthetics 
    A_overall_neg = A_streetscape_neg + A_sidewalk_neg + A_aes_neg, # Negative SAS
    A_overall = A_overall_pos - A_overall_neg # Overall SAS 1 
    )
# add A3_ prefix back to variable names
A3 <- A %>% 
  rename_with(~gsub("A_", "A3_", .x))

# A4 --------------------------------------------------------------------------
# select only School Access Segment variables and rename, ensure the order of variable names matches data set
A <- maps %>% 
  select(c(starts_with("A4_"),"SchoolID" )) %>%
  setNames( c("A_00Street", "A_00Side", "A_00Start", 
              "A__00End", "A_01", "A_02","A_03", "A_04",
              "A_05", "A_06","A_07", "A_08", "A_09", 
              "A_10", "A_11", "A_12", "A_13", "A_14", 
              "A_15a", "A_15b", "A_16a", "A_16b", 
              "A_16c", "A_16d", "A_17a", "A_17b", "A_17c",
              "A_17d", "A_17e", "A_17f", "A_18a", "A_18b", 
              "A_18c", "A_18d", "A_18e", "A_19a", "A_19b",
              "A_19c", "A_19d", "A_20a", "A_20b", "A_20c", "A_21", 
              "A_22", "SchoolID"))
# Create subscales
A <- A %>%
  mutate(
    A_calming_pos = case_when(A_16a == 1 | A_16b == 1 | A_16c == 1 | A_16d == 1 ~ 1, # Positive streetscape subscale
                              A_16a == 0 & A_16b == 0 & A_16c == 0 & A_16d == 0 ~ 0),
    A_lights_pos = case_when(A_02 == 1 | A_02 == 2 | A_03 == 1 | A_03 == 2 ~ 1,
                             A_02 == 0 & A_03 == 0 ~ 0),
    A_driveways_pos = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 1,
                                A_21 == 4 ~ 0),
    A_speed_dichot = case_when(A_13 == 5 | A_13 == 4 | A_13 == 3 | A_13 == 2 | A_13 == 1 ~ 1, 
                               A_13 == 0 ~ 0),
    A_speed25_pos = case_when(A_13 == 5 | A_13 == 4 ~ 1,
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 0),
    A_speed_spec_pos = case_when(A_14 == 3 | A_14 == 2 | A_14 == 1 ~ 1,
                                    A_14 == 0 ~ 0),
    A_signs_pos = A_17a + A_17b + A_17c + A_17d,
    A_streetscape_pos = 
           A_01 + 
           A_calming_pos + 
           A_lights_pos +
           A_driveways_pos +
           A_20a +
           A_20b +
           A_20c +
           A_speed_dichot + 
           A_speed25_pos +
           A_speed_spec_pos +
           A_signs_pos,
    A_sidewalk = case_when(A_07 == 2 | A_07 == 3 ~ 2, # Positive sidewalk subscale
                           A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_cont = case_when(A_07 == 3 ~ 1,
                                A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 0),
    A_sidewalk_width = case_when(A_08 == 3 ~ 3,
                                 A_08 == 2 | A_08 == 1 ~ 2,
                                 A_08 == -777 ~ 0),
    A_sidewalk_pos = A_sidewalk + A_sidewalk_cont + A_sidewalk_width,
    A_buffer_pos = case_when(A_10 == 1 ~ 1, # Positive buffer
                             A_10 == 0 | A_10 == -777 ~ 0), 
    A_bike_pos = case_when(A_06 == 5 | A_06 == 4 ~ 2, # Bike infrastructure 
                           A_06 == 3 | A_06 == 2 ~ 1,
                           A_06 == 1 | A_06 == 0 ~ 0), 
    A_trees_pos = case_when(A_11 == 2 ~ 2, # Shade
                            A_11 == 1 ~ 1,
                            A_11 == 0 | A_11 == -777 ~ 0), 
    A_awning_pos = case_when(A_12 == 2 ~ 2,
                             A_12 == 1 ~ 1,
                             A_12 == 0 | A_12 == -777 ~ 0),
    A_shade_pos = A_trees_pos + A_awning_pos,
    A_overall_pos = A_streetscape_pos + # Positive SAS
           A_sidewalk_pos + 
           A_buffer_pos + 
           A_bike_pos + 
           A_shade_pos,
    A_speed25_neg = case_when(A_13 == 5 | A_13 == 4 ~ 0, # Negative streetscape
                              A_13 == 3 | A_13 == 2 | A_13 == 1 | A_13== 0 ~ 1), 
    A_driveways_neg = case_when(A_21 == 1 | A_21 == 2 | A_21 == 3 ~ 0,
                                A_21 == 4 ~ 1),
    A_streetscape_neg = A_speed25_neg + A_driveways_neg,
    A_cont_neg = case_when(A_07 == 3 ~ 0,
                           A_07 == 2 | A_07 == 1 | A_07 == 0 ~ 1), # Negative sidewalk
    A_trip_neg = case_when(A_09 == 1 | A_09 == 2 | A_09 ==-777 ~ 0,
                           A_09 == 3 | A_09 == 4 ~ 1),
    A_sidewalk_neg = A_cont_neg + A_trip_neg, 
    A_aes_neg = case_when(A_05 = 1 | A_05 == 2 | A_05 == 3 ~ 1,
                          A_05 == 0 ~ 0), #Negative aesthetics 
    A_overall_neg = A_streetscape_neg + A_sidewalk_neg + A_aes_neg, # Negative SAS
    A_overall = A_overall_pos - A_overall_neg # Overall SAS 1 
    )
# add A4_ prefix back to variable names
A4 <- A %>% 
  rename_with(~gsub("A_", "A4_", .x))

# combine school access segments 1 - 4 in a single data frame
combined_A <- cbind(A1, A2, A3, A4)
```

```{r 4. Subscale scoring for segments}
# S1 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S1_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S1 <- S %>% 
  rename_with(~gsub("S_", "S1_", .x))

# S2 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S2_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S2 <- S %>% 
  rename_with(~gsub("S_", "S2_", .x))

# S3 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S3_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S3 <- S %>% 
  rename_with(~gsub("S_", "S3_", .x))

# S4 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S4_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S4 <- S %>% 
  rename_with(~gsub("S_", "S4_", .x))

# S5 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S5_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S5 <- S %>% 
  rename_with(~gsub("S_", "S5_", .x))

# S6 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S6_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S6 <- S %>% 
  rename_with(~gsub("S_", "S6_", .x))

# S7 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S7_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S7 <- S %>% 
  rename_with(~gsub("S_", "S7_", .x))

# S8 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S8_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S8 <- S %>% 
  rename_with(~gsub("S_", "S8_", .x))

# S9 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S9_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S9 <- S %>% 
  rename_with(~gsub("S_", "S9_", .x))

# S10 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S10_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S10 <- S %>% 
  rename_with(~gsub("S_", "S10_", .x))

# S11 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S11_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S11 <- S %>% 
  rename_with(~gsub("S_", "S11_", .x))

# S12 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S12_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c", 
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S12 <- S %>% 
  rename_with(~gsub("S_", "S12_", .x))

# S13 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S13_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c",
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20", 
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S13 <- S %>% 
  rename_with(~gsub("S_", "S13_", .x))

# S14 --------------------------------------------------------------------------
# select only segment variables and rename, ensure the order of variable names matches data set 
S <- maps %>% 
  select(c(starts_with("S14_"),"SchoolID" )) %>%
  setNames(c("S_00Street", "S_00Side", "S_00Start", 
             "S_00End", "S_01", "S_02","S_03",
             "S_04","S_05", "S_06","S_07", "S_08",
             "S_09", "S_10", "S_11", "S_12", "S_13a",
             "S_13b", "S_14a", "S_14b", "S_14c",
             "S_14d",  "S_15a", "S_15b", "S_15c",
             "S_15d", "S_15e", "S_15f", "S_16a",
             "S_16b", "S_16c", "S_16d", "S_16e",
             "S_17a", "S_17b", "S_17c", "S_17d",
             "S_18a", "S_18b", "S_18c", "S_19", "S_20",
             "SchoolID"))
# Create subscales
S <- S %>%
  mutate(
    S_calming_pos = case_when(S_14a == 1 | S_14b == 1 | S_14c == 1 | S_14d == 1 ~ 1, # Positive streetscape subscale
                              S_14a == 0 & S_14b == 0 & S_14c == 0 & S_14d == 0 ~ 0),
    S_lights_pos = case_when(S_02 == 1 | S_02 == 2 | S_03 == 1 | S_03 == 2 ~ 1,
                             S_02 == 0 & S_03 == 0 ~ 0),
    S_driveways_pos = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 1,
                                S_19 == 4 ~ 0),
    S_speed_dichot = case_when(S_13a == 5 | S_13a == 4 | S_13a == 3 | S_13a == 2 | S_13a == 1 ~ 1, 
                               S_13a == 0 ~ 0),
    S_speed25_pos = case_when(S_13a == 5 | S_13a == 4 ~ 1,
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 0),
    S_speed_spec_pos = case_when(S_13b == 5 |S_13b == 4 |S_13b == 3 | S_13b == 2 | S_13b == 1 ~ 1,
                                    S_13b == 0 ~ 0),
    S_signs_pos = S_15a + S_15b + S_15c + S_15d + S_15e + S_15f,
    S_streetscape_pos = 
           S_01 + 
           S_calming_pos + 
           S_lights_pos +
           S_driveways_pos +
           S_18a +
           S_18b +
           S_18c +
           S_speed_dichot + 
           S_speed25_pos +
           S_speed_spec_pos +
           S_signs_pos,
    S_sidewalk = case_when(S_07 == 2 | S_07 == 3 ~ 2, # Positive sidewalk subscale
                           S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_cont = case_when(S_07 == 3 ~ 1,
                                S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 0),
    S_sidewalk_width = case_when(S_08 == 3 ~ 3,
                                 S_08 == 2 | S_08 == 1 ~ 2,
                                 S_08 == -777 ~ 0),
    S_sidewalk_pos = S_sidewalk + S_sidewalk_cont + S_sidewalk_width,
    S_buffer_pos = case_when(S_10 == 1 ~ 1, # Positive buffer
                             S_10 == 0 | S_10 == -777 ~ 0), 
    S_bike_pos = case_when(S_06 == 5 | S_06 == 4 ~ 2, # Bike infrastructure 
                           S_06 == 3 | S_06 == 2 ~ 1,
                           S_06 == 1 | S_06 == 0 ~ 0), 
    S_trees_pos = case_when(S_11 == 2 ~ 2, # Shade
                            S_11 == 1 ~ 1,
                            S_11 == 0 | S_11 == -777 ~ 0), 
    S_awning_pos = case_when(S_12 == 2 ~ 2,
                             S_12 == 1 ~ 1,
                             S_12 == 0 | S_12 == -777 ~ 0),
    S_shade_pos = S_trees_pos + S_awning_pos,
    S_overall_pos = S_streetscape_pos + # Positive segment
           S_sidewalk_pos + 
           S_buffer_pos + 
           S_bike_pos + 
           S_shade_pos,
    S_speed25_neg = case_when(S_13a == 5 | S_13a == 4 ~ 0, # Negative streetscape
                              S_13a == 3 | S_13a == 2 | S_13a == 1 | S_13a == 0 ~ 1), 
    S_driveways_neg = case_when(S_19 == 1 | S_19 == 2 | S_19 == 3 ~ 0,
                                S_19 == 4 ~ 1),
    S_streetscape_neg = S_speed25_neg + S_driveways_neg,
    S_cont_neg = case_when(S_07 == 3 ~ 0,
                           S_07 == 2 | S_07 == 1 | S_07 == 0 ~ 1), # Negative sidewalk
    S_trip_neg = case_when(S_09 == 1 | S_09 == 2 | S_09 ==-777 ~ 0,
                           S_09 == 3 | S_09 == 4 ~ 1),
    S_sidewalk_neg = S_cont_neg + S_trip_neg, 
    S_aes_neg = case_when(S_05 == 0 ~ 0, 
                          S_05 = 1 | S_05 == 2 | S_05 == 3 ~ 1), #Negative aesthetics 
    S_overall_neg = S_streetscape_neg + S_sidewalk_neg + S_aes_neg, # Negative segment
    S_overall = S_overall_pos - S_overall_neg # Overall Segment 1 
    )

S14 <- S %>% 
  rename_with(~gsub("S_", "S14_", .x))

# combine all segments --------------------------------------------------------
combined_S <- cbind(S1, S2, S3, S4, S5, S6, S7, S8, S9, S10, S11, S12, S13, S14)
```

```{r 5. Subscale scoring for crossings}
# C1 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C1_"),"SchoolID" )) %>%
  setNames(c( "C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C1 <- C %>% 
  rename_with(~gsub("C_", "C1_", .x))

# C2 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C2_"),"SchoolID" )) %>%
  setNames(c( "C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C2 <- C %>% 
  rename_with(~gsub("C_", "C2_", .x))
# C3 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C3_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C3 <- C %>% 
  rename_with(~gsub("C_", "C3_", .x))
# C4 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C4_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C4 <- C %>% 
  rename_with(~gsub("C_", "C4_", .x))

# C5 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C5_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C5 <- C %>% 
  rename_with(~gsub("C_", "C5_", .x))
# C6 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C6_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C6 <- C %>% 
  rename_with(~gsub("C_", "C6_", .x))
# C7 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C7_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C7 <- C %>% 
  rename_with(~gsub("C_", "C7_", .x))
# C8 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C8_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C8 <- C %>% 
  rename_with(~gsub("C_", "C8_", .x))

# C9 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C9_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C9 <- C %>% 
  rename_with(~gsub("C_", "C9_", .x))
# C10 --------------------------------------------------------------------------
# select only crossing variables and rename, ensure the order of variable names matches data set 
C <- maps %>% 
  select(c(starts_with("C10_"),"SchoolID" )) %>%
  setNames(c("C_01a", "C_01b","C_01bi","C_00Intersection1","C_00Intersection2",
         "C_00Direction1","C_00Direction2","C_01bii", "C_01c",
         "C_00Crossing1", "C_00Crossing2", "C_00Crossing3",
         "C_02a", "C_02b", "C_02c", "C_02d","C_03a",
         "C_03b", "C_03c", "C_03d", "C_04a", "C_04b",
         "C_05a", "C_05b", "C_05c", "C_05d", "C_06a",
         "C_06b", "C_06c", "C_07", "C_08", "C_09a",
         "C_09b", "C_09c", "C_00Notes", "SchoolID"))
# Create subscales
C <- C %>%
  mutate(
    C_amenities_pos = # crosswalk amenities
      C_05a + 
      C_05b +
      C_05c +
      C_05d +
      C_06a +
      C_06b +
      C_06c,
    C_pre_curb_pos = case_when(C_04a == 1 ~ 1, # curb ramps positive
                               C_04a == 2 | C_04a ==3 ~ 0),
    C_post_curb_pos = case_when(C_04b == 1 ~ 1,
                                C_04b == 2 | C_04b ==3 ~ 0),
    C_curb_qual_pos = C_pre_curb_pos + C_post_curb_pos,
    C_control_pos = # intersection control
      C_02a +
      C_02b +
      C_02c +
      C_02d +
      C_03a +
      C_03b +
      C_03c +
      C_03d,
    C_overall_pos = C_amenities_pos + C_curb_qual_pos + C_control_pos, # positive crossing
    C_width = case_when(C_07 == 1 | C_07 == 2 ~ 0, # road width
                        C_07 == 3 | C_07 == 4 ~ 1,
                        C_07 == 5 | C_07 == 6 | C_07 == 7 ~ 2),
    C_pre_curb_neg = case_when(C_04a == 1 | C_04a == 2 ~ 0, # curb ramps negative
                               C_04a ==3 ~ 1),
    C_post_curb_neg = case_when(C_04b == 1 | C_04b == 2 ~ 0,
                                C_04b ==3 ~ 1),
    C_imped =  # crossing impediments
      C_pre_curb_neg + 
      C_post_curb_neg +
      C_09a + 
      C_09b,
    C_overall_neg =  C_width + C_imped, # negative crossing
    C_overall = C_overall_pos - C_overall_neg # overall crossing
  )
C10 <- C %>% 
  rename_with(~gsub("C_", "C10_", .x))

# combine all crossing
combined_C <- cbind(C1, C2, C3, C4, C5, C6, C7, C8, C9, C10)
```

```{r 6. MEANS - Combine subscales and create functions for aggregation}
# combine all sections back into one data frame
maps_scored <- cbind(combined_A, combined_S, combined_C)

# create function for row means by subscale 
subscale_mean <- function(df, section, subscale, var_name)  {
    df %>%
      select(starts_with(section) & ends_with(subscale)) %>%
      mutate(!!quo_name(var_name) := rowMeans(., na.rm = TRUE))
}
```

```{r 7. MEANS - Scoring for school access segment aggregate scores}
# school access segments subscale means
A_calming_pos_mean <- subscale_mean(maps_scored, "A", "calming_pos","A_calming_pos_mean")
A_lights_pos_mean <- subscale_mean(maps_scored, "A", "lights_pos","A_lights_pos_mean")
A_driveways_pos_mean <- subscale_mean(maps_scored, "A", "driveways_pos","A_driveways_pos_mean")
A_speed_dichot_mean <- subscale_mean(maps_scored, "A", "speed_dichot","A_speed_dichot_mean")
A_speed25_pos_mean <- subscale_mean(maps_scored, "A", "speed25_pos","A_speed25_pos_mean")
A_speed_spec_pos_mean <- subscale_mean(maps_scored, "A", "speed_spec_pos","A_speed_spec_pos_mean")
A_signs_pos_mean <- subscale_mean(maps_scored, "A", "signs_pos","A_signs_pos_mean")
A_streetscape_pos_mean <- subscale_mean(maps_scored, "A", "streetscape_pos","A_streetscape_pos_mean")
A_sidewalk_mean <- subscale_mean(maps_scored, "A", "sidewalk","A_sidewalk_mean")
A_sidewalk_cont_mean <- subscale_mean(maps_scored, "A", "sidewalk_cont","A_sidewalk_cont_mean")
A_sidewalk_width_mean <- subscale_mean(maps_scored, "A", "sidewalk_width","A_sidewalk_width_mean")
A_sidewalk_pos_mean <- subscale_mean(maps_scored, "A", "sidewalk_pos","A_sidewalk_pos_mean")
A_buffer_pos_mean <- subscale_mean(maps_scored, "A", "buffer_pos","A_buffer_pos_mean")
A_bike_pos_mean <- subscale_mean(maps_scored, "A", "bike_pos","A_bike_pos_mean")
A_trees_pos_mean <- subscale_mean(maps_scored, "A", "trees_pos","A_trees_pos_mean")
A_awning_pos_mean <- subscale_mean(maps_scored, "A", "awning_pos","A_awning_pos_mean")
A_shade_pos_mean <- subscale_mean(maps_scored, "A", "shade_pos","A_shade_pos_mean")
A_overall_pos_mean <- subscale_mean(maps_scored, "A", "overall_pos","A_pos_mean")
A_speed25_neg_mean <- subscale_mean(maps_scored, "A", "speed25_neg","A_speed25_neg_mean")
A_driveways_neg_mean <- subscale_mean(maps_scored, "A", "driveways_neg","A_driveways_neg_mean")
A_streetscape_neg_mean <- subscale_mean(maps_scored, "A", "streetscape_neg","A_streetscape_neg_mean")
A_cont_neg_mean <- subscale_mean(maps_scored, "A", "cont_neg","A_cont_neg_mean")
A_trip_neg_mean <- subscale_mean(maps_scored, "A", "trip_neg","A_trip_neg_mean")
A_sidewalk_neg_mean <- subscale_mean(maps_scored, "A", "sidewalk_neg","A_sidewalk_neg_mean")
A_aes_neg_mean <- subscale_mean(maps_scored, "A", "aes_neg","A_aes_neg_mean")
A_overall_neg_mean <- subscale_mean(maps_scored, "A", "overall_neg","A_neg_mean")
A_overall_mean <- subscale_mean(maps_scored, "A", "overall","A_overall_mean")

# combine all school access segment mean data frames
A_means_all <- cbind(A_calming_pos_mean, 
                 A_lights_pos_mean,
                 A_driveways_pos_mean,
                 A_speed_dichot_mean,
                 A_speed25_pos_mean,
                 A_speed_spec_pos_mean,
                 A_signs_pos_mean,
                 A_streetscape_pos_mean,
                 A_sidewalk_mean,
                 A_sidewalk_cont_mean,
                 A_sidewalk_width_mean,
                 A_sidewalk_pos_mean,
                 A_buffer_pos_mean,
                 A_bike_pos_mean,
                 A_trees_pos_mean,
                 A_awning_pos_mean,
                 A_shade_pos_mean,
                 A_overall_pos_mean,
                 A_speed25_neg_mean,
                 A_driveways_neg_mean,
                 A_streetscape_neg_mean,
                 A_cont_neg_mean,
                 A_trip_neg_mean,
                 A_sidewalk_neg_mean,
                 A_aes_neg_mean,	
                 A_overall_neg_mean,
                 A_overall_mean)
# filter for just the mean variables
A_means <- A_means_all %>%
  select(ends_with("mean"))
```

```{r 8. MEANS - Scoring for segment aggregate scores}
# segments subscale means
S_calming_pos_mean <- subscale_mean(maps_scored, "S", "calming_pos","S_calming_pos_mean")
S_lights_pos_mean <- subscale_mean(maps_scored, "S", "lights_pos","S_lights_pos_mean")
S_driveways_pos_mean <- subscale_mean(maps_scored, "S", "driveways_pos","S_driveways_pos_mean")
S_speed_dichot_mean <- subscale_mean(maps_scored, "S", "speed_dichot","S_speed_dichot_mean")
S_speed25_pos_mean <- subscale_mean(maps_scored, "S", "speed25_pos","S_speed25_pos_mean")
S_speed_spec_pos_mean <- subscale_mean(maps_scored, "S", "speed_spec_pos","S_speed_spec_pos_mean")
S_signs_pos_mean <- subscale_mean(maps_scored, "S", "signs_pos","S_signs_pos_mean")
S_streetscape_pos_mean <- subscale_mean(maps_scored, "S", "streetscape_pos","S_streetscape_pos_mean")
S_sidewalk_mean <- subscale_mean(maps_scored, "S", "sidewalk","S_sidewalk_mean")
S_sidewalk_cont_mean <- subscale_mean(maps_scored, "S", "sidewalk_cont","S_sidewalk_cont_mean")
S_sidewalk_width_mean <- subscale_mean(maps_scored, "S", "sidewalk_width","S_sidewalk_width_mean")
S_sidewalk_pos_mean <- subscale_mean(maps_scored, "S", "sidewalk_pos","S_sidewalk_pos_mean")
S_buffer_pos_mean <- subscale_mean(maps_scored, "S", "buffer_pos","S_buffer_pos_mean")
S_bike_pos_mean <- subscale_mean(maps_scored, "S", "bike_pos","S_bike_pos_mean")
S_trees_pos_mean <- subscale_mean(maps_scored, "S", "trees_pos","S_trees_pos_mean")
S_awning_pos_mean <- subscale_mean(maps_scored, "S", "awning_pos","S_awning_pos_mean")
S_shade_pos_mean <- subscale_mean(maps_scored, "S", "shade_pos","S_shade_pos_mean")
S_overall_pos_mean <- subscale_mean(maps_scored, "S", "overall_pos","S_pos_mean")
S_speed25_neg_mean <- subscale_mean(maps_scored, "S", "speed25_neg","S_speed25_neg_mean")
S_driveways_neg_mean <- subscale_mean(maps_scored, "S", "driveways_neg","S_driveways_neg_mean")
S_streetscape_neg_mean <- subscale_mean(maps_scored, "S", "streetscape_neg","S_streetscape_neg_mean")
S_cont_neg_mean <- subscale_mean(maps_scored, "S", "cont_neg","S_cont_neg_mean")
S_trip_neg_mean <- subscale_mean(maps_scored, "S", "trip_neg","S_trip_neg_mean")
S_sidewalk_neg_mean <- subscale_mean(maps_scored, "S", "sidewalk_neg","S_sidewalk_neg_mean")
S_aes_neg_mean <- subscale_mean(maps_scored, "S", "aes_neg","S_aes_neg_mean")
S_overall_neg_mean <- subscale_mean(maps_scored, "S", "overall_neg","S_neg_mean")
S_overall_mean <- subscale_mean(maps_scored, "S", "overall","S_overall_mean")

# combine all segment mean data frames
S_means_all <- cbind(S_calming_pos_mean, 
                 S_lights_pos_mean,
                 S_driveways_pos_mean,
                 S_speed_dichot_mean,
                 S_speed25_pos_mean,
                 S_speed_spec_pos_mean,
                 S_signs_pos_mean,
                 S_streetscape_pos_mean,
                 S_sidewalk_mean,
                 S_sidewalk_cont_mean,
                 S_sidewalk_width_mean,
                 S_sidewalk_pos_mean,
                 S_buffer_pos_mean,
                 S_bike_pos_mean,
                 S_trees_pos_mean,
                 S_awning_pos_mean,
                 S_shade_pos_mean,
                 S_overall_pos_mean,
                 S_speed25_neg_mean,
                 S_driveways_neg_mean,
                 S_streetscape_neg_mean,
                 S_cont_neg_mean,
                 S_trip_neg_mean,
                 S_sidewalk_neg_mean,
                 S_aes_neg_mean,	
                 S_overall_neg_mean,
                 S_overall_mean)
# filter for just the mean variables
S_means <- S_means_all %>%
  select(ends_with("mean"))
```

```{r 9. MEANS - Scoring for crossing aggregate scores}
# crossing subscale means
C_amenities_pos_mean <- subscale_mean(maps_scored, "C", "amenities_pos","C_amenities_pos_mean")
C_pre_curb_pos_mean <- subscale_mean(maps_scored, "C", "pre_curb_pos","C_pre_curb_pos_mean")
C_post_curb_pos_mean <- subscale_mean(maps_scored, "C", "post_curb_pos","C_post_curb_pos_mean")
C_curb_qual_pos_mean <- subscale_mean(maps_scored, "C", "curb_qual_pos","C_curb_qual_pos_mean")
C_control_pos_mean <- subscale_mean(maps_scored, "C", "control_pos","C_control_pos_mean")
C_overall_pos_mean <- subscale_mean(maps_scored, "C", "overall_pos","C_overall_pos_mean")
C_width_mean <- subscale_mean(maps_scored, "C", "width","C_width_mean")
C_pre_curb_neg_mean <- subscale_mean(maps_scored, "C", "pre_curb_neg","C_pre_curb_neg_mean")
C_post_curb_neg_mean <- subscale_mean(maps_scored, "C", "post_curb_neg","C_post_curb_neg_mean")
C_imped_mean <- subscale_mean(maps_scored, "C", "imped","C_imped_mean")
C_overall_neg_mean <- subscale_mean(maps_scored, "C", "overall_neg","C_overall_neg_mean")
C_overall_mean <- subscale_mean(maps_scored, "C", "overall","C_overall_mean")

# combine all crossing mean data frames
C_means_all <- cbind(C_amenities_pos_mean,
                     C_pre_curb_pos_mean,
                     C_post_curb_pos_mean,
                     C_curb_qual_pos_mean,
                     C_control_pos_mean,
                     C_overall_pos_mean,
                     C_width_mean,
                     C_pre_curb_neg_mean,
                     C_post_curb_neg_mean,
                     C_imped_mean,
                     C_overall_neg_mean,
                     C_overall_mean)

# filter for just the mean variables
C_means <- C_means_all %>%
  select(ends_with("mean"))
```

```{r 10. MEANS - Add mean scores back to main data frame and export data}
#remove duplicate variables
maps_with_dup <- cbind(maps_scored, A_means, S_means, C_means)
maps_unique <- maps_with_dup[!duplicated(as.list(maps_with_dup))]

# combine with STREETS school info variables
school_info <- maps %>%
  select(qc, cohort, timepoint, schertz, arm)
maps_final <- cbind(school_info, maps_unique)

write.csv(maps_final, "streets_maps.csv")
```

```{r 11. Inter rater reliability analyses}
# IRR data set up ------------------------------------------------------------
maps_final$SchoolID <- gsub("_QC","",maps_final$SchoolID) #remove _QC from schoolid values
maps_qc <- maps_final %>% # Select only QC schools
  filter(qc == 1 | qc == 2)  

# ICC for school access segments ---------------------------------------------
a_overall_icc <- maps_qc %>%
  select(A_overall_mean, qc, SchoolID) %>% # select variable for ICC, plus qc and schoolid grouping variable
  pivot_wider(names_from = qc, values_from = A_overall_mean) %>% # make data wide
  select("1","2") # remove schoolid
icc(a_overall_icc, model = "oneway", type = "agreement")

# ICC for segments -----------------------------------------------------------
s_overall_icc <- maps_qc %>%
  select(S_overall_mean, qc, SchoolID) %>%
  pivot_wider(names_from = qc, values_from = S_overall_mean) %>%
  select("1","2")
icc(s_overall_icc, model = "oneway", type = "agreement")

# ICC for crossings ----------------------------------------------------------
c_overall_icc <- maps_qc %>%
  select(C_overall_mean, qc, SchoolID) %>%
  pivot_wider(names_from = qc, values_from = C_overall_mean) %>%
  select("1","2")
icc(c_overall_icc, model = "oneway", type = "agreement")


```

```{r 12. Summary tables and data visualizations}
# Assess distributions of overall variables 
# Select only overall scores and convert to long
overall_values <- maps_final%>%
  select("A_overall_mean", "S_overall_mean", "C_overall_mean")
melt_overall <- melt(overall_values)

# plot all three variables 
 ggplot(data = melt_overall, aes(x = value)) + 
   geom_histogram() + 
   facet_wrap(~variable, scales = "free")
```